---
title: "Project 4 - Example Main Script"
author: "Jing Wu, Tian Zheng"
date: "3/22/2017"
output: pdf_document
---

In this project, we implement one of the suggested papers, Culotta (2007). 

## Step 0: Load the packages, specify directories

```{r}
packages.used=c("plyr","text2vec","qlcMatrix","kernlab")

# check packages that need to be installed.
packages.needed=setdiff(packages.used, 
                        intersect(installed.packages()[,1], 
                                  packages.used))
# install additional packages
if(length(packages.needed)>0){
  install.packages(packages.needed, dependencies = TRUE,
                   repos='http://cran.us.r-project.org')
}

library(plyr)
library(text2vec)
library(qlcMatrix)
library(kernlab)
```
## Step 1: Load and process the data

For each record in the dataset, there are some information we want to extract and store them in a regular form: canonical author id, coauthors, paper title, publication venue title. You may need to find regular matched in the input string vectors by using regex in R. Here is a tutorial for regular expression in R, which might help you <https://rstudio-pubs-static.s3.amazonaws.com/74603_76cd14d5983f47408fdf0b323550b846.html>

```{r}
#function for data pre-processing
create_data <- function(filename){
  #name <- deparse(substitute(filename))
  tmp <- read.csv(filename,
                  header = F,
                  sep = "\n")    
  rule = "<([[:alpha:]]|[[:punct:]]){1,4}>"
  tmp$V1 = gsub(rule,"",tmp$V1)
  rule1 = ">([[:alpha:]]){1,5}:"
  tmp$V1 = gsub(rule1,">",tmp$V1)
  Sys.setlocale('LC_ALL','C')
  L = strsplit(tmp$V1,split = ">")
  tmp$Coauthor = laply(L,function(t) t[1])
  tmp$Paper = laply(L,function(t) t[2])
  tmp$Journal = laply(L,function(t) t[3])
  
  # extract canonical author id befor "_"
  tmp$AuthorID <- as.numeric(sub("_.*","",tmp$Coauthor))
  # extract paper number under same author between "_" and first whitespace
  tmp$PaperNO <- as.numeric(sub(".*_(\\w*)\\s.*", "\\1", tmp$Coauthor))
  # delete "<" in AKumar$Coauthor, you may need to further process the coauthor
  # term depending on the method you are using
  tmp$Coauthor <- gsub("<","",sub("^.*?\\s","", tmp$Coauthor))
  # delete "<" in AKumar$Paper
  tmp$Paper <- gsub("<","",tmp$Paper)
  # add PaperID for furthur use, you may want to combine all the nameset files and 
  # then assign the unique ID for all the citations
  tmp$PaperID <- rownames(tmp)
  return(tmp)
}
```

```{r}
## apply function
setwd("../data/nameset")
file_names <- list.files(pattern = "*.txt")
Data = list()
for(i in 1:length(file_names)){
  Data[[i]]= create_data(file_names[i])
}
names(Data) = file_names
```

## Step 2: Feature design

Following the section 3.1 in the paper, we want to use paper titles to design features for citations. As the notation used in the paper, we want to find a $m$-dimensional citation vector $\alpha_i$ for each citation $i$, $i=1,...,n$. In this dataset, $n=$ `r nrow(AKumar)`. We study "TF-IDF" (term frequency-inverse document frequency) as suggested in the paper.

TF-IDF is a numerical statistics that is intended to reflect how important a word is to a document in a collection or corpus. It is often used as a weighting factor in information retrieval, text mining, and user modeling. The TF-IDF value increases proportionally to the number of times a word appears in the document, but is offset by the frequency of the word in the corpus, which helps to adjust for the fact that some words appear more frequently in general.

$$
\begin{aligned}
\mbox{TF}(t) &=\frac{\mbox{Number of times term $t$ appears in a document}}{\mbox{Total number of terms in the document}}\\
\mbox{IDF}(t) &=\log{\frac{\mbox{Total number of documents}}{\mbox{Number of documents with term $t$ in it}}}\\
\mbox{TF-IDF}(t) &=\mbox{TF}(t)\times\mbox{IDF}(t)
\end{aligned}
$$

To compute TF-IDF, we first need to construct a document-term matrix (DTM). In other words, the first step is to vectorize text by creating a map from words to a vector space. There are some good packages you could use for text mining (probably you have tried during first project, you don't need to follow my code if you are familiar with other package), e.g. *text2vec, tm, tidytext*. Here, we are going to use *text2vec* package. A good tutorial can be found here, <https://cran.r-project.org/web/packages/text2vec/vignettes/text-vectorization.html>.

Let???s first create a vocabulary-based DTM. Here we collect unique terms from all documents and mark each of them with a unique ID using the  `create_vocabulary()` function. We use an iterator to create the vocabulary.
```{r}
it_train <- itoken(Data[[1]]$Paper,
             preprocessor = tolower, 
             tokenizer = word_tokenizer,
             ids = Data[[1]]$PaperID,
             # turn off progressbar because it won't look nice in rmd
             progressbar = FALSE)
vocab <- create_vocabulary(it_train, stopwords = c("a", "an", "the", "in", "on",
                                                   "at", "of", "above", "under"))

vocab
```

Here, we remove pre-defined stopwords, the words like a, the, in, I, you, on, etc, which do not provide much useful information. 

Now that we have a vocabulary list, we can construct a document-term matrix.
```{r}
vectorizer <- vocab_vectorizer(vocab)
dtm_train <- create_dtm(it_train, vectorizer)
```

Now we have DTM and can check its dimensions.
```{r}
dim(dtm_train)
```

As you can see, the DTM has `r nrow(dtm_train)` rows, equal to the number of citations, and `r ncol(dtm_train)`, equal to the number of unique terms excluding stopwords.

Then, we want to use DTM to compute TF-IDF transformation on DTM.
```{r}
tfidf <- TfIdf$new()
dtm_train_tfidf <- fit_transform(dtm_train, tfidf)
Fea_wol <- as.matrix(dtm_train_tfidf)
Fea_wl = cbind(label = unlist(Data[[1]]$AuthorID),Fea_wol)
#ocsdissim_test <- as.matrix(cosSparse(t(dtm_train_tfidf)))
```

## Step 3: Clustering

Following suggestion in the paper, we carry out hierarchical clustering on the matrix of the citation vectors.The number of clusters for the Agupta example is assumed known as 26.  
### First Iteration  

```{r}
start.time <- Sys.time()
## initialize lamda
lamda = rep(1/ncol(dtm_train_tfidf),ncol(dtm_train_tfidf))
## First partition is that each article is a individual cluster
###(1) our score of N^(1)
sum(Fea_wol%*%lamda)
###(2) try to get the F1 score
## a = 0, b = 0
## count of match of golden standard: c = 
w = 1:max(as.numeric(Data[[1]]$PaperID))
df = expand.grid(w,w)
df = df[(df[,1]>df[,2]),]
y = Fea_wl[,1]
c = sum(y[df[,1]] == y[df[,2]])

## count of mismatch of golden standard: d = 
d = choose(nrow(Fea_wol),2) - c
## Precision and recall and F1
## Since percision is 0/0, move on to 
end.time <- Sys.time()
t =end.time-start.time
```  

###Iterate over the clustering methods  

```{r}
start.time <- Sys.time()
w = 1:nrow(Fea_wol)
df2 = expand.grid(w,w)
df2 = df2[(df2[,1]>df2[,2]),]
#loop for score and F1 for each possible combination using df2
score2<- c()
F1_2<-c()
for (i in 1:nrow(df2)){
  r1=df2[i,1]
  r2=df2[i,2]
  new<- rbind(Fea_wol[r1,], Fea_wol[r2,])
  new<- colMeans(new)
  newdf<- rbind(Fea_wol[-c(r1,r2),], new)
  score2[i]=sum(newdf%*%lamda)
  
}


end.time <- Sys.time()
time_sclust <- end.time - start.time
table(result_sclust)
```  

## calculate the match and mismatch of G
```{r}
a_c = 0
for(i in 1:nrow(df)){
 q1 = df[i,1]
 q2 = df[i,2]
 a_c = a_c + (y[q1]==y[q2])
}
b_d = choose(nrow(Data[[1]]),2)-a_c
```
## Update Lamda  

```{r}
## Generate different partition method
grid = 1:nrow(Fea_wol)
partition = expand.grid(grid,grid)
partition = partition[( partition[,1] > partition[,2]),]
column = seq(1,nrow(Data[[1]]))
labels = matrix(column, nrow=length(column), ncol= nrow(partition)) 
for(i in 1:nrow(partition)){
  # Compute our prediction
  label_us=labels[,i]
  label_us = label_us + 1
  # r1 = partition[i,][1]
  # r2 = partition[i,][1]
  r1 <- partition$Var1[i]
  r2 <- partition$Var2[i]
  label_us[r1] = 1
  label_us[r2] = 1
  labels[,i]=label_us
}
# for calculating F1
a_b <- 0
a_c <-0
F1 = rep(NA,ncol(labels))
for(j in 1:ncol(labels) ){
  for(k in 1:nrow(df)){
    q1 <- df[k,1]
    q2 <- df[k,2]
    #a_b means a+b, c_d means c+d
    a_b <- a_b+(labels[q1,j]==labels[q2,j])
    c_d <- choose(nrow(Data[[1]]),2)-a_b
    a = -c_d+a_c+b_d
    precision = a/a_b
    recall = a/a_c
    F1 [j]= (2*precision*recall)/(precision+recall)
  }
}

#function for computing score, input is dataframe "labels"
# get_score <- function(label_i){
#     Fea_wol_1 <- data.frame(cbind(Fea_wol,label_1=label_i))
#     Fea_wol_1 <- aggregate(Fea_wol_1,by=list(Fea_wol_1$label_1),FUN=mean)
#     score <- sum((as.matrix(Fea_wol_1[,-c(1,ncol(Fea_wol_1))])%*%lamda))
# }
# score <- aaply(labels,2,get_score)
```


We can also using hierarchical clustering method under the cosine distance. The intention of using a different clustering method is just to let you know how to compare performance between various methods. 
```{r}
start.time <- Sys.time()
docsdissim <- cosSparse(t(dtm_train_tfidf))
rownames(docsdissim) <- c(1:nrow(dtm_train_tfidf))
colnames(docsdissim) <- c(1:nrow(dtm_train_tfidf))
#compute pairwise cosine similarities using cosSparse function in package qlcMatrix
h <- hclust(as.dist(docsdissim), method = "ward.D")
result_hclust <- cutree(h,length(unique(Data[[1]]$AuthorID)))
end.time <- Sys.time()
time_hclust <- end.time - start.time
table(result_hclust)
```

## Step 4: Evaluation

To evaluate the performance of the method, it is required to calculate the degree of agreement between a set of system-output partitions and a set of true partitions. In general, the agreement between two partitioins is measured for a pair of entities within partitions. The basic unit for which pair-wise agreement is assessed is a pair of entities (authors in our case) which belongs to one of the four cells in the following table (Kang et at.(2009)):

\includegraphics[width=500pt]{matching_matrix.png}

Let $M$ be the set of machine-generated clusters, and $G$ the set of gold standard clusters. Then. in the table, for example, $a$ is the number of pairs of entities that are assigned to the same cluster in each of $M$ and $G$. Hence, $a$ and $d$ are interpreted as agreements, and $b$ and $c$ disagreements. When the table is considered as a confusion matrix for a two-class prediction problem, the standard "Precision", "Recall","F1", and "Accuracy" are defined as follows.

$$
\begin{aligned}
\mbox{Precision} &=\frac{a}{a+b}\\
\mbox{Recall}&=\frac{a}{a+c}\\
\mbox{F1} &=\frac{2\times\mbox{Precision}\times\mbox{Recall}}{\mbox{Precision}+\mbox{Recall}}\\
\mbox{Accuracy}&=\frac{a+d}{a+b+c+d}
\end{aligned}
$$

```{r}
source("../lib/evaluation_measures.R")
matching_matrix_hclust <- matching_matrix(AKumar$AuthorID,result_hclust)
performance_hclust <- performance_statistics(matching_matrix_hclust)
matching_matrix_sclust <- matching_matrix(AKumar$AuthorID,result_sclust)
performance_sclust <- performance_statistics(matching_matrix_sclust)
compare_df <- data.frame(method=c("sClust","hClust"),
                         precision=c(performance_sclust$precision, performance_hclust$precision),
                         recall=c(performance_sclust$recall, performance_hclust$recall),
                         f1=c(performance_sclust$f1, performance_hclust$f1),
                         accuracy=c(performance_sclust$accuracy, performance_hclust$accuracy),
                         time=c(time_sclust,time_hclust))
kable(compare_df,caption="Comparision of performance for two clustering methods",digits = 2)
```

